Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Corrected the projection of Figure 13

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 10) +
  theme(
    aspect.ratio = 1
  )

@@

## First projection
# projection <- cbind(
#   c(0.02743,0.21427,0.62893,-0.49816),
#   c(-0.70709,0.42156,-0.02593,0.10965))
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

@@

error_df_gau_pacmap <- error_df_gau_abs |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(-0.02, 0.18)) + ylim(c(0.12, 0.32)) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  interior_annotation("c3", 
                      position = c(0.08, 0.9),
                      cex = 2)

>>>>

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  theme(
    aspect.ratio = 1
  )

@@

## First projection
# projection <- cbind(
#   c(0.02743,0.21427,0.62893,-0.49816),
#   c(-0.70709,0.42156,-0.02593,0.10965))
# projection <- cbind(
#   c(-0.00215,-0.68905,-0.04778,-0.54223),
#   c(0.42558,-0.23854,-0.63659,0.35753))

projection <- cbind(
  c(-0.04778, -0.54223, -0.00215, -0.68905),
  c(-0.63659, 0.35753, 0.42558, -0.23854))

@@

error_df_gau_pacmap <- error_df_gau_abs |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.6,
             size = 1.5) + 
  xlim(c(-0.02, 0.18)) + ylim(c(0.12, 0.32)) +
  scale_colour_continuous_sequential(palette = "YlOrRd", breaks = 20) +
  interior_annotation("c3", 
                      position = c(0.08, 0.9),
                      cex = 2)
